D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
OOTA from UB: Wordsmith
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Please note that the OOTA-like cycle called out in the \co{exists}
clause can happen even though the program never actually executes any
code that would have resulted in division-by-zero UB.
It is tempting to consider using techniques
% Appendix~\ref{app:Aside on Undefined Behavior}
that prevent back-propagation of UB, but these are ineffective in this
case because the compiler can detect and exploit UB when
considering line~14 in isolation.
Once the constant 1 is substituted for line~14's expression, the
hardware is free to reorder lines~13 and~14 even if a compiler-based
C++ implementation refrains from doing so.
Note that this OOTA-like cycle can appear even if all of the atomic
operations in
Listing~\ref{lst:OOTA Due To Divide-By-Zero UB}
were converted to be volatile.

>>>>

Please note that the OOTA-like cycle called out in the \co{exists}
clause can happen even though the program never actually executes any
code that would have resulted in division-by-zero UB.
It is tempting to consider using techniques
% Appendix~\ref{app:Aside on Undefined Behavior}
that prevent back-propagation of UB, but these are ineffective in this
case because the compiler can detect and exploit UB when
considering line~14 in isolation.
Once the constant 1 is substituted for line~14's expression, the
hardware is free to reorder lines~13 and~14 even if a compiler-based
C++ implementation refrains from doing so.
Note that this OOTA-like cycle can appear even if all of the atomic
operations in
Listing~\ref{lst:OOTA Due To Divide-By-Zero UB}
are converted to volatile.
